\HeaderA{multivariateAnomaly}{Anomaly detection in time-series measurements}{multivariateAnomaly}
\begin{Description}\relax
Performs anomaly detection using algorithm descriped in the referenced paper, for a set of multivariate time series predictor values and a set of target values.
\end{Description}
\begin{Usage}
\begin{verbatim}
multivariateAnomaly(X, Y, r, sig, nv, d = 0.1)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{X}] The predictor time series variables, each row is a variable and each column is a timestamp.

\item[\code{Y}] The target time series.

\item[\code{r}] The autoregression lag.

\item[\code{sig}] The spread width of the RBF kernel.

\item[\code{nv}] Number of eigenvectors to be used.

\item[\code{d}] The damping factor to be passed to the anomaly detection function. Default value is 0.1

\end{ldescription}
\end{Arguments}
\begin{Value}
Intermediate outputs produced in this step passed to anomaly detection function

\begin{ldescription}
\item[\code{w}] The weight associated with each eigenvector.

\item[\code{KX}] The new aligned kernel matrix for X.

\item[\code{KY}] The kernel matrix for target Y.

\end{ldescription}
\end{Value}
\begin{Author}\relax
Sriram Lakshminarasimhan
Siddarth Ramaswamy
\end{Author}
\begin{References}\relax
[1] Haibin Cheng, Pang-Ning Tan, Christopher Potter, and Steven Klooster. 
A Robust Graph-based Algorithm for Detection and Characterization of Anomalies in Noisy
Multivariate Time Series, to appear in Proc.of IEEE International Conference on Data Mining
workshop on Spatial and Spatio-temporal Data Mining (ICDM/STDM 08)
\end{References}
\begin{Examples}
\begin{ExampleCode}
# X is the predictor, having 2 variables whose values have been measured from
# t1 to t5 . Y is the target variable.
data(KernelPredictorSample2)
data(KernelTargetSample2)
X = as.matrix(KernelPredictorSample2)
Y = as.matrix(KernelTargetSample2)
X
Y
# multivariateAnomaly function takes in input target and predictor matrices, 
# along with the number of eigen values and the spread width of the RBF kernel.
# Damping factor is an optional parameter.
RandomWalkOutput = multivariateAnomaly(X, Y, 0, 93.14, 5)
RandomWalkOutput
\end{ExampleCode}
\end{Examples}

